Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
ok

**Augment data** (geocoordinates, gender, ..)

@@

@@

\Large{1. General trends and political events}

@@

[General trends & political events]

@@

        	geom_point(data = subset(dfw, !highlight2 == 1),
      	    aes(
      	      thickness = 10,
      	      x = longitude, 
      	      y = latitude,
	            shape = 19, 
	            #shape = highlight2, 
	            color = highlight), 
      	      colour = "black", 
      	      shape = 21, # Point shape 
      	      size = 7,   # Point size
      	      stroke = 2) + # Point edge thickness

@@

 riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
 cols = c("pink", "Purple", "aquamarine", "yellow")
 rectangles$shade[rectangles$shade == "Highlight"] = riksplace
 rectangles$shade = factor(rectangles$shade)

@@

\Large{2. Publishers in Sweden and Turku}

@@

[Publishers in Sweden and Turku]

@@

\begin{center}
[Publishers in Sweden and Turku]
\end{center}

@@

# Title count per decade & publisher	
npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
#npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
# Sort by biggest publication decade
#ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher
ord <- as.character((npub %>% group_by(publisher) %>% 
                        summarise(decade = median(publication_decade)) %>% 
                        arrange(decade))$publisher)
npub$publisher <- factor(npub$publisher, levels = ord)

@@

\Large{3. Languages and religious texts in Finland}

@@

[Languages & religious texts in Finland]

@@

p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
       geom_line() + geom_point() + ylab("Documents (n)") + xlab("Publication year")

@@

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(catalogue) 
       #ggtitle(paste("Languages (", catalogue, ")", sep = "")) 
  print(p)
```

@@

\Large{4. University curriculum and Enlightenment in Finland}

@@

[University curriculum & Enlightenment in Finland]

@@

@@

>>>>

**Enrich data** (geocoordinates, gender, ..)

@@

- Parse, clean up, enrich, summarise, analyze, visualize, report..

@@

\begin{center}
\Large{1. General trends and political events}
\end{center}

@@

\begin{center}
\tiny{\textcolor{gray}{General trends \& political events}}
\end{center}

@@

        	geom_point(data = subset(dfw, !highlight2 == 1),
      	    aes(
      	      thickness = 10,
      	      x = longitude, 
      	      y = latitude,
	            shape = 19, 
	            #shape = highlight2, 
	            color = highlight), 
      	      colour = "black", 
      	      shape = 21, # Point shape 
      	      size = 7,   # Point size
      	      stroke = 1.5) + # Point edge thickness

@@

 riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
 cols = c("white", "Purple", "blue", "orange")
 rectangles$shade[rectangles$shade == "Highlight"] = riksplace
 rectangles$shade = factor(rectangles$shade)

@@

\begin{center}
\Large{2. Publishers in Sweden and Turku}
\end{center}

@@

\begin{center}
\tiny{\textcolor{gray}{Publishers in Sweden and Turku}}
\end{center}

@@

\begin{center}
\tiny{\textcolor{gray}{Publishers in Sweden and Turku}}
\end{center}

@@

# Title count per decade & publisher	
npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
#npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
# Sort by biggest publication decade
#ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher
ord <- as.character((npub %>% group_by(publisher) %>% 
                        summarise(decade = median(publication_decade)) %>% 
                        arrange(decade))$publisher)
npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))

@@

\begin{center}
\Large{3. Languages and religious texts in Finland}
\end{center}

@@

\begin{center}
\tiny{\textcolor{gray}{Languages \& religious texts in Finland}}
\end{center}

@@

p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
       geom_line() + geom_point() + 
       geom_smooth(aes(fill = language, color = language)) + 
       ylab("Documents (n)") + xlab("Publication year")

@@

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       #geom_smooth(aes(fill = language, color = language)) + 
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(catalogue) 
       #ggtitle(paste("Languages (", catalogue, ")", sep = "")) 
  print(p)
```

@@

\begin{center}
\Large{4. University curriculum and Enlightenment in Finland}
\end{center}

@@

\begin{center}
\tiny{\textcolor{gray}{University curriculum \& Enlightenment in Finland}}
\end{center}

@@

Code infrastructure:

- Github
- R project

@@

\begin{figure}
\begin{tabular}{cccccc}
\includegraphics[width=2cm,height=2cm]{aka.png}&
\includegraphics[width=1cm,height=1cm]{HY-CC.png}&
\includegraphics[width=1cm,height=1cm]{kansalliskirjasto.png}&
\includegraphics[width=1cm,height=1cm]{kungliga.png}&
\includegraphics[width=1cm,height=1cm]{github-logo.png}
\end{tabular}
\end{figure}
